---
title: "p8105_hw1_yg3096"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moderndive)
library(ggplot2)
library(dplyr)
library(tidyverse)
data("early_january_weather")
```

## Problem 1
The data has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.      
Variables names are: `r paste(names(early_january_weather), collapse = ", ")`.    
And the average temperature is `r round(mean(early_january_weather$temp, na.rm = TRUE), 2)`.
```{r}
# Plot temperature vs time, using color of points to show humidity
p <- ggplot(early_january_weather, aes(x = time_hour, y = temp, 
                                       color = humid)) +
     geom_point() + labs(x = "Date", y = "Temperature", color = "Humidity",
                         title = "Temperature vs Time (colored by humidity)")
print(p)

# Save the plot
ggsave(filename = "plot.png", plot = p)
```
The plot shows that the temperature has a overall trend of increasing. Also,    
the change of temperature in a single day has a periodic pattern.

## Problem 2
```{r}
set.seed(123)

# A random sample of size 10 from a standard normal distribution
norm_sample <- rnorm(10)

# A logical vector indicating whether elements of the sample are greater than 0
logical_vec <- norm_sample > 0

# A character vector of length 10
char_vec <- c("a","b","c","d","e","f","g","h","i","j")

# A factor vector of length 10 with 3 different factor levels
factor_vec <- factor(sample(c("low","medium","high"), 10, replace = TRUE), 
                     levels = c("low","medium","high"))

df <- data.frame(norm_sample = norm_sample, logical_vec = logical_vec,
                  char_vec = char_vec, factor_vec = factor_vec)

mean_norm <- mean(df %>% pull(norm_sample)) # working, returns 0.07462564
mean_logical <- mean(df %>% pull(logical_vec)) # working, returns 0.5
# Not working: mean_char and mean_factor

# Logical to numeric
as.numeric(df$logical_vec) # TRUE -> 1, FALSE -> 0

# Factor to numeric
as.numeric(df$factor_vec) # returns (1,2,3), not the specific level

# character to numeric (only if the character can be transfred into numbers)
# as.numeric(df$char_vec) works if char_vec contains "1", "2"... 
```