---
title: "p8105_hw1_yg3096"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(moderndive)
library(ggplot2)
library(dplyr)
data("early_january_weather")
```

## Problem 1
The data has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.      
Variables names are: `r paste(names(early_january_weather), collapse = ", ")`.    
And the average temperature is `r round(mean(early_january_weather$temp, na.rm = TRUE), 2)`.
```{r}
# Plot temperature vs time, using color of points to show humidity
p <- ggplot(early_january_weather, aes(x = time_hour, y = temp, 
                                       color = humid)) +
     geom_point() + labs(x = "Date", y = "Temperature", color = "Humidity",
                         title = "Temperature vs Time (colored by humidity)")
print(p)

# Save the plot
ggsave(filename = "plot.png", plot = p)
```
The plot shows that the temperature has a overall trend of increasing. Also,    
the change of temperature in a single day has a periodic pattern.